---
title: "Mario"
author: "Mario"
date: '2020-11-02'
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)  
library(vegan)
library(emmeans)
setwd("/R Packages/Magic The Gathering")
```

## Load Magic Dataset
The following dataset was compiled by opening 15 draft booster boxes from recent Magic the Gathering Standard sets. 5 Boxes of Ikoria: Lair of Behemoths, 5 of Core 2021, and 5 of Zendikar Rising. Packs were opened and all cards inputted for the exception of tokens and basic land cards.
```{r cars}
MTG <- read.csv("MTG_data.csv")
MTG <- MTG %>%
  group_by(set, rep, card_name, rarity, card_type, finish, n, price) %>%
  summarise(total = sum(n))
MTG_norep <- MTG %>%
  group_by(set, card_name, rarity, card_type, finish, n, price) %>%
  summarise(total = sum(n))
```

##Vegan Set-up
```{r}
###Group main Data by Set, Rarity, Card Type, Finish, Total number and Price. Rep was removed from this dataset.
MTG_Vegan <- MTG_norep %>%
  group_by(set, rarity, card_type, card_name, finish, total, price) 

MTG_Vegan$rarity <- gsub(" ", "", MTG_Vegan$rarity)
MTG_Vegan$rarity <- as.factor(MTG_Vegan$rarity)
MTG_Vegan$uniID <- paste(MTG_Vegan$set, MTG_Vegan$rarity)
str(MTG_Vegan)

###Ungroup all and select the Unique ID, n, and total of specific card per box
library(dplyr)
MTG_Vegan <- MTG_Vegan %>% 
  ungroup()%>%
  dplyr::select(uniID, n, total)
MTG_Vegan <- MTG_Vegan %>% group_by(uniID, total) %>% summarise(Total = sum(n))

MTG_Vegan
###Spread the Data
commMTG <- MTG_Vegan %>% spread(total, Total)
commMTG[is.na(commMTG)] <- 0

##Drop Unique ID
commMTG <- commMTG %>%
  ungroup() %>%
  dplyr::select(-uniID)

commMTG

##Set up a mini-dataset to join the calculations to after. This dataset broken up by set and rarity.
setMTG <- MTG %>%
  group_by(set, rarity) %>%
  summarise(Total = sum(n))

setMTG$Total <- gsub(" ", "", setMTG$Total)
setMTG$Total <- as.factor(setMTG$Total)
setMTG$uniID <- paste(setMTG$set, setMTG$rarity)
str(setMTG)

setMTG <- setMTG %>%
  ungroup()%>%
  dplyr::select(uniID, set, rarity, Total)
setMTG <- setMTG %>% group_by(uniID, rarity)

setMTG <- setMTG %>%
  ungroup() %>%
  dplyr::select(-uniID)

##Run Simpsons test and Evenness for community data
##Note: Since many Mythics were only pulled ONCE during openings, many of the Simpsons and evenness calculations for Mythic cards result in either a 0 or NA
simpsonfinal <- diversity(commMTG, index = "simpson")
Hfinal <- diversity(commMTG)
Sfinal <- specnumber(commMTG)
Evenness <- Hfinal/log(Sfinal) 
setMTG$Simpson <- simpsonfinal
setMTG$Evenness <- Evenness

##Merge Data back to the main dataset
finalMTG <- merge(MTG_norep, setMTG)
```
```{r}
###Card Price Setup
MTGPrice <- read_csv("MTG_data.csv")
packprice <- MTGPrice %>%
  group_by(set, rep, pack_rep) %>%
  summarise(x = sum(price))
boxprice <- MTGPrice %>%
  group_by(set, rep) %>%
  summarise(x = sum(price))

packprice$pack_rep <- as.factor(packprice$pack_rep)
packprice$rep <- as.factor(packprice$rep)
boxprice$rep <- as.factor(boxprice$rep)
names(packprice)[4] <- "Total_Value"
names(boxprice)[3] <- "Total_Value"

```
###Data Viz
```{r}
###Figure showing Total cards rarities pulled by set
count <- ggplot(setMTG, aes(set, Total, fill = set)) +
  geom_histogram(stat = "identity") +
  facet_wrap(~rarity) +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Set", y = "Total Cards by Rarity")
count
```
```{r}
type <- ggplot(finalMTG, aes(card_type, total, fill = set)) +
  geom_histogram(stat = "identity") +
  facet_wrap(~rarity) +
  theme_classic() + 
  theme(axis.text.x = element_text( 
                           size = 12, angle = 90))+
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Card Type", y = "Total Cards by Card Type")
type
```
```{r}
cardtype <- finalMTG %>%
 group_by(set, rarity, card_type, n) %>%
  summarise(total_type = sum(total), n = n()) 

###Displays all card types pulled in each set
ggplot(cardtype, aes(card_type, n, fill = set)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(fill = "", x = "Card Type", y = "Total Number of Cards")


###Displays all card types pulled in each set by Rarity
ggplot(cardtype, aes(card_type, n, fill = rarity)) +
  geom_bar(stat = "identity") +
  facet_wrap(~set) +
  coord_flip() + 
  labs(fill = "", x = "Card Type", y = "Total Number of Cards")
 

```
```{r}
###Boxplot showing the total number of cards pulled by card type, filled by set.(Shows that creature is the most significant card type. See m4 stats.)
ggplot(cardtype, aes(card_type, total_type, fill = set)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(fill = "", x = "Card Type", y = "Total Number of Cards") +theme_classic()
###Tried running the above image as a boxplot but does not look too appealing.
ggplot(cardtype, aes(card_type, total_type, color = set)) +
  geom_boxplot() +theme_classic() + ylab("Total Number of Cards") + xlab("Card Type") +theme(axis.text.x = element_text(angle = 90))
```
```{r}
##Total rarity by evenness
Evenness <- ggplot(finalMTG, aes(total, Evenness, color = rarity)) + 
  geom_point(size = 1.5) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Box Number", y = "Evenness")
Evenness

###Total rarity by simpsons index
Richness <- ggplot(finalMTG, aes(total, Simpson, color = rarity)) + 
  geom_point(size = 1.5) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Set1") + theme_classic() + 
  geom_smooth(method = lm, se = TRUE) + 
  labs(x = "Box Number", y = "Simpson Index")
Richness
```

```{r}
ggplot(cardtype, aes(set, total_type, color = card_type)) +
  geom_boxplot() 
ggplot(cardtype, aes(set, total_type, color = rarity)) +
  geom_boxplot() 
ggplot(cardtype, aes(rarity, total_type)) +
  geom_boxplot() 
###Boxplot showing the total cards by rarity filled by set.
ggplot(cardtype, aes(rarity, total_type, color = set)) +
  geom_boxplot() +theme_classic() + ylab("Total Number of Cards") + xlab("Card Rarity")
```

```{r}
###Tried to put the previous figure as a barplot but not the biggest fan of the way this one looks.
ggplot(cardtype, aes(rarity, total_type, fill = set)) +
  geom_bar(stat = "identity") +
  coord_flip() + 
  labs(fill = "", x = "Card Rarity", y = "Total Number of Cards") +theme_classic()
```
```{r}
ggplot(packprice, aes(pack_rep, Total_Value, fill = set)) +
  geom_boxplot() +
  labs(fill = "", x = "Pack Number", y = "Total Value") +theme_classic() + theme(axis.text.x = element_text(angle = 90))
###Plot of Pack values
ggplot(packprice, aes(pack_rep, Total_Value, fill = set)) +
  geom_bar(stat = "identity") +
  labs(fill = "", x = "Pack Number", y = "Total Value") +theme_classic() + theme(axis.text.x = element_text(angle = 90))
ggplot(packprice, aes(rep, Total_Value, fill = set)) +
  geom_boxplot() +
  labs(fill = "", x = "Box Number", y = "Total Value") +theme_classic()
###Plots of Box values
ggplot(boxprice, aes(rep, Total_Value, fill = set)) +
  geom_bar(stat = "identity") +
  labs(fill = "", x = "Box Number", y = "Total Valuer") +theme_classic()
#Plot showing value of each set
ggplot(boxprice, aes(set, Total_Value, fill = set)) +
  geom_boxplot() +
  labs(fill = "", x = "Box Number", y = "Total Value") +theme_classic()
```
###Stats
```{r}
###Total number of cards by set and rarity. (Seems rarity is significant, but no significance in post-hoc analysis)
m1 <- glm(total_type ~ set*rarity, family = "quasipoisson", data = cardtype)
anova(m1, test = "Chisq")
e1 <- emmeans(m1, pairwise~set|rarity)
e1
```
```{r}
###Total number of cards by just rarity (there is a significance but that is because each pack has a set number of commons, uncommons, and rares)
m2 <- glm(total_type ~ rarity, family = "quasipoisson", data = cardtype)
anova(m2, test = "Chisq")
e2 <- emmeans(m2, pairwise~rarity)
e2
```
```{r}
###Significance in terms of card type by set
m3 <- glm(total_type ~ set*card_type, family = "quasipoisson", data = cardtype)
anova(m3, test = "Chisq")
e3 <- emmeans(m3, pairwise~set|card_type)
e3
``` 

```{r}
###Shows significance in terms of card type. emmeans shows that there is significnce between creatures and all other card types in the game.
m4 <- glm(total_type ~ card_type, family = "quasipoisson", data = cardtype)
anova(m4, test = "Chisq")
e4 <- emmeans(m4, pairwise~card_type)
e4
```
```{r}
###Stats for significance between each box by set (Ran as a poisson). 
m5 <- glm(Total_Value ~ set*rep, family = "poisson", data = boxprice)
anova(m5, test = "Chisq")
e5 <- emmeans(m5, pairwise~set*rep)
e5
```
```{r}
###Stats for overall value of each set. (Shows that there is a significance between sets. Significance Between Ikoria and Core 2021, and Core 2021 and Zendikar Rising)
m6 <- glm(Total_Value ~ set, family = "quasipoisson", data = boxprice)
anova(m6, test = "Chisq")
e6 <- emmeans(m6, pairwise~set)
e6
```
```{r}
##Statistics showing the significance between Boxes pulled for each set. There is significance between some of the boxes with Ikoria seeming to have the higher Total values compared to certain other boxes from other sets.
m7 <- glm(Total_Value ~ set*rep, family = "poisson", data = boxprice)
anova(m7, test = "Chisq")
e7 <- emmeans(m7, pairwise~set*rep)
e7
```
```{r}
###Statistics showing difference in Total Values based on pack number (No significance)
m8 <- glm(Total_Value ~ pack_rep, family = "quasipoisson", data = packprice)
anova(m8, test = "Chisq")
e8 <- emmeans(m8, pairwise~pack_rep)
e8
```
```{r}
###Stats showing significance of Total value from a pack based on the set. Seems to be some significance but not sure how important this information is. (Went through all post-hoc p-values, none were significant)
m9 <- glm(Total_Value ~ pack_rep*set, family = "quasipoisson", data = packprice)
anova(m9, test = "Chisq")
e9 <- emmeans(m9, pairwise~pack_rep*set)
e9
```
###Findings:
1) Pulling creature type cards seems to be much higher than pulling any of the other card types in the game (m4 stats). All other card types show no significance between one another.
2) There was seen to be no significant difference between pulling a rare card and mythic card in these sets (m2 stats), while there is a significance between common and rare cards(Most likely since every pack has 9 commons and 1 Rare). However there was no significance between common and mythic cards which seems really strange.
3) There is significance in the overal value of the 3 sets. Core 2021 had the lowest value pulled from all boxes when compared to Ikoria and Zendikar rising, while there is no significant difference between Ikoria and Zendikar Rising.
4) Purchasing a box of Ikoria is better than purchasing a box of any of the other sets???